### 2018-08-08 paper/evaluation.tex
ended eval

In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the file transfer performance in section~\ref{sub:file_transfer}.

@@

\subsubsection{Availability of nodes and messages in transit} % (fold)
\label{ssub:traffic_and_availability}

@@

  \caption{\label{fig:avail}
  Availability of devices and number of messages waiting for reception.}
\end{figure}

@@

An obvious direction for future work is to implement at Time To Leave (TTL) or other stale-messages-removal policy.

\\
To conclude this section, we have seen that \name could empower users to privately exchange files over a challenging network where only 15.8\% of the infrastructure was available at a time.
Our proposal, \name, allows to nevertheless complete the file exchange with an average probability of 94.4\%, against 41.7\% success rate using classical onion routes

>>>>

In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the file transfer performance in section~\ref{sub:file_transfer}. Finally, we look at the devices availability over time, and at the messages life over the network in \ref{ssub:traffic_and_availability}.

@@

\subsection{Availability of nodes and messages in transit} % (fold)
\label{ssub:traffic_and_availability}

@@

  \caption{\label{fig:avail}
  Availability of devices (in gray) and number of messages waiting for reception (in black) over an experiment. The black dotted line represents the mean rate of online devices: 15.8\%.}
\end{figure}

@@

An obvious direction for future work is to implement at Time To Leave (TTL) or other stale-messages-removal policy.
\\

We have seen that \name could empower users to privately exchange files in a distributed manner over a challenging network where only 15.8\% of the infrastructure is available at a time.
Our proposal allows to nevertheless complete the file exchange with an average probability of 94.4\%, against 41.7\% success rate using classical onion routes.
